Giant Low Surface Brightness Galaxies As Merger Remnants

### 2016-11-17 glsb.tex

\author{Peter Yoachim\altaffilmark{1}, Denise Schmitz\altaffilmark{4}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{5}, Victor P. Debattista\altaffilmark{3}
  }

\altaffiltext{1}{Department of Astronomy, University of Washington, Box 351580,
Seattle WA, 98195}
\altaffiltext{2}{University of Michigan}
\altaffiltext{3}{Jeremiah Horrocks Institute, University of Central Lancashire, Preston PR1 2HE, UK.}
\altaffiltext{4}{California Institute of Technology}
\altaffiltext{5}{Center for the Exploration of the Origin of the Universe
(CEOU), Department of Physics \& Astronomy, Seoul
National University, Seoul 151-742, Republic of Korea}

>>>>

\author{Peter Yoachim\altaffilmark{1}, Denise Schmitz\altaffilmark{4}, Sarah Loebman\altaffilmark{2}, SungWon Kwak\altaffilmark{5,6}, Victor P. Debattista\altaffilmark{3}
  }

\altaffiltext{1}{Department of Astronomy, University of Washington, Box 351580,
Seattle WA, 98195}
\altaffiltext{2}{University of Michigan}
\altaffiltext{3}{Jeremiah Horrocks Institute, University of Central Lancashire, Preston PR1 2HE, UK.}
\altaffiltext{4}{California Institute of Technology}
\altaffiltext{5}{Center for the Exploration of the Origin of the Universe
(CEOU), Department of Physics \& Astronomy, Seoul
National University, Seoul 151-742, Republic of Korea}
\altaffiltext{6}{Korea Astronomy and Space Science Institute, Daejeon 305-348, Republic of Korea}
